Changes in Faculty Composition and Stagnating State Support for Higher Education

### 2023-03-20 text/sections/06-discussion.tex
Finished major revision.  Needs more checks of writing style.

The data used so far measure faculty count, so cannot disentangle which of these channels is most affected by changes in state funding at a public university, yet \cite{wapman2022quantifying} provide a measure of the aggregated total faculty hires at universities over the time period 2011--2021.\footnote{
    \citep{wapman2022quantifying} made an aggregated version of their data open-source, making this sub-analysis possible.
}
\begin{figure}[h!]
    \centering
    \singlespacing
    \caption{State Funding and Faculty Hired at Public Universities, Total for 2011--2021.}
    \includegraphics[width=0.95\textwidth]{figures/hiring-correlation.png}
    \label{fig:hiring-correlation.png}
\end{figure}

Universities with more state funding (for the entire decade) hired more professors (\autoref{fig:hiring-correlation.png}).
Similarly, the funding shock instrument identifies that an increase in 10\% state funding leads to 13 more faculty hires across the decade 2011--2021, without any clear difference between the genders (\autoref{tab:hiring-shock-reg}).\footnote{
    These results were produced by integrating the total count of faculty hires for 2010--2021 for the top-ranked 180 US universities with a sum of the funding variables, and then estimating the models specified in \autoref{sec:iv-model-uni}.
    See \autoref{sec:appendix-hiring} for further details.
}
It is clear that public universities' hiring is negatively impacted by falls in state funding, even using these aggregated data for count of hiring. 
While this analysis strengthens the case negative effects on hiring plays, it is crude for measuring exact magnitudes for the effect on faculty hiring; I leave it to further research to delve deeper into the magnitudes that hiring plays as the primary causal mediator for the effects on faculty composition of falls in state funding for public universities.

>>>>

The data used so far measure faculty count, so cannot disentangle which of these channels is most affected by changes in state funding at a public university, yet \cite{wapman2022quantifying} provide a measure of the aggregated total faculty hires at universities over the time period 2011--2021.\footnote{
    \citep{wapman2022quantifying} made an aggregated version of their data open-source, making this sub-analysis possible.
}
\begin{figure}[h!]
    \centering
    \singlespacing
    \caption{State Funding and Faculty Hired at Public Universities, Total for 2011--2021.}
    \includegraphics[width=0.8\textwidth]{figures/hiring-correlation.png}
    \label{fig:hiring-correlation.png}
\end{figure}

Universities with more state funding (for the entire decade) hired more professors (\autoref{fig:hiring-correlation.png}).
Similarly, the funding shock instrument identifies that an increase in 10\% state funding at an individual university leads to 13 more faculty hires on average across the decade 2011--2021 (see \autoref{tab:hiring-shock-reg}).\footnote{
    These results were produced by integrating the total count of faculty hires for 2010--2021 for the top-ranked 180 US universities with a sum of the funding variables, and then estimating the models specified in \autoref{sec:iv-model-uni}.
    There were no observable differences in the hiring rate of ale vs female faculty.
    See \autoref{sec:appendix-hiring} for further details.
}
It is clear that public universities' hiring is negatively impacted by falls in state funding, even using highly aggregated data for a total count of hiring across an entire decade.
While this analysis strengthens the case negative effects on hiring plays, it is crude for measuring exact magnitudes for the effect on faculty hiring; I leave it to further research to delve deeper into the magnitudes that hiring plays as the primary causal mediator for the effects of falls in state funding on faculty composition at public universities.
